Article title

### 2017-06-28 paper-webserver.tex
ADD: grammer + 5th para

The surveillance of bacterial pathogens is a routine function of public-health agencies. In \textit{Salmonella enterica} \cite{bell2016recent}, \textit{Escherichia coli} \cite{fratamico2016advances}, and others pathogens \cite{ronholm2016navigating}, culture-dependent subtyping techniques are becoming displaced by culture-independent methods based on whole-genome sequencing (WGS). Secondary analyses, the study of relations and historical relevance of genomes, are now possible on large datasets due to WGS \cite{ronholm2016navigating}. Advances in WGS technologies have also enabled the monitoring and sharing of outbreak genomes in real-time \cite{ronholm2016navigating}.

@@

Previously we developed Superphy \cite{whiteside2016superphy}, an online platform, targeting \textit{E. coli}, which determines Shiga toxin subtypes, AMR genes using the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and provides statistical significance tests between subgroups in associated metadata. Here we present Spfy, a complete rewrite of Superphy integrating our Panseq package \cite{laing2010pan} for pan-genomic analyses of accessory regions, long-term storage of results in a graph database, and containerization of services using Docker, a modern approach found in many web servers and proposed to mitigate the complexities of bioinformatic pipelines \cite{di2015impact}. Furthermore, Spfy takes a modular approach to tool integration and distributes analyses over task queues, thereby allowing modules to run in parallel. All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

Spfy enables processing of thousands of genome sequences using multiple modules. By using task queue workers, enabled by the Python-based Redis Queue library, performance can quickly scale to available infrastructure. As a bioinformatics tool, we ensured reliability of the platform by integrating the open-source Sentry toolkit for real-time exception tracking. The use of Docker-Compose for orchestrating containers ensures that the entire platform, webservers, databases, and task workers, can be easily replicated by other researchers. We present Spfy as a template for brining advances in web application development and deployment to online bioinformatics platforms.

>>>>

The surveillance of bacterial pathogens is a routine function of public-health agencies. In \textit{Salmonella enterica} \cite{bell2016recent}, \textit{Escherichia coli} \cite{fratamico2016advances}, and others pathogens \cite{ronholm2016navigating}, culture-dependent subtyping techniques are becoming displaced by culture-independent methods based on whole-genome sequencing (WGS). Secondary analyses, the study of relations and historical relevance of genomes, are now possible on large datasets provided by WGS \cite{ronholm2016navigating}. Advances in WGS technologies have also enabled the monitoring and sharing of outbreak genomes in real-time \cite{ronholm2016navigating}.

@@

Previously we developed Superphy \cite{whiteside2016superphy}, an online platform targeting \textit{E. coli}, which determines Shiga toxin subtypes, Antimicrobial Resistance (AMR) genes using the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and provides statistical significance tests between subgroups in associated metadata. Here we present Spfy, a complete rewrite of Superphy integrating our Panseq package \cite{laing2010pan} for pan-genomic analyses of accessory regions, long-term storage of results in a graph database, and containerization of services using Docker, a modern approach found in many web servers and proposed to mitigate the complexities of bioinformatic pipelines \cite{di2015impact}. Furthermore, Spfy takes a modular approach to tool integration and distributes analyses over task queues, thereby allowing modules to run in parallel. All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

Spfy enables processing of thousands of genome sequences using multiple modules. By using task queue workers, enabled by the Python-based Redis Queue library \url{https://github.com/nvie/rq}, performance can quickly scale to available infrastructure. As a bioinformatics tool, we ensured reliability of the platform by integrating the open-source Sentry toolkit \url{https://github.com/getsentry/sentry} for real-time exception tracking. Containers are orchestrated through Docker-Compose allowing the entire platform: webservers, databases, and task workers, to be easily replicated by other researchers. We present Spfy as a template for brining advances in web application development and deployment to online bioinformatics platforms.

We designed Spfy's front-end following the Material Design standards \url{https://material.io/}, released by Google. The user interface is implemented with the React JavaScript library \url{https://facebook.github.io/react/}, as a single-page application to allow efficient data-flow without reloading the website. Everything is compartmentalized within separate Docker containers where the front-end is networked, through Docker-Compose, to the back-end webserver.
